Rule-Based Normalization of German Twitter Messages

### 2013-08-28 darmstadt_gscl_2013/article_twitter_normalization.tex
related work partially expanded

Among works belonging to the NCM framework, we could mention the
approach suggested by Mayes, Damerau et al. (\cite{mayes}) who used a
uniform error model and calculated $P(S)$ on the basis of word bigrams
statistics. As a set $S$ of possible replacement suggestions, the
authors regarded the original input word $T$ as well as all words in
dictionary which could be derived from the original word by applying
at most one edit operation either insertion, or deletion, or
substituion of a single character. In \cite{church}, Church and Gale
suggested a more elaborated error model in which every edit operation
was weihgted according to statistics gathered from a training corpus
and conditioned on the letter context in which this edit operation
apeeared. Brill and Moore (\cite{Brill}) further enhanced this model
by considering edit operations not only on single letters but rather
on word subsegments of different lengths. Toutanova and Moore
(\cite{toutanova}) improved the performance of the latter work by
23~\% by incorporating phonetical information. Eventually, Alexander
Clark (\cite{clark}) was one among the first who addressed the text
noisiness problem in the genre of Internet-based communication
(IBC). In his presented system, multiple indpendent modules were used
to perform tokenization, normalization and correction of Usenet forum
posts. The system relied on a 3-gram language model and a trainable
stateless stochastic transduces as error model, however no particular
details about its implementation were provided in the article. In
\cite{choudhury}, Choudhury et al. proposed

>>>>

Among works belonging to the NCM framework, we could mention the approach
suggested by Mayes, Damerau et al. (\cite{mayes}) who used a uniform error
model and calculated $P(S)$ on the basis of word bigrams statistics. As a set
$S$ of possible replacement suggestions, the authors regarded the original
input word $T$ as well as all words in dictionary which could be derived from
$T$ by applying at most one edit operation which could be either insertion, or
deletion, or substituion of a single character or a transposition of two
adjacent characters. In \cite{church}, Church and Gale suggested a more
elaborated error model in which they weighted every edit operation according
to statistics generated from a training corpus and additionally conditioned
each of these operations on the letter context in which they appeared. Brill
and Moore (\cite{Brill}) enhanced this model by considering edit operations
not only for single letters but for whole word subsegments up to a length of 5
characters. Toutanova and Moore (\cite{toutanova}) improved the performance of
the latter work by 23~\% by incorporating phonetical information in
it. Eventually, Alexander Clark (\cite{clark}) was one among the first who
addressed the text noisiness problem in the genre of Internet-based
communication (IBC). In his presented system, multiple independent modules
were used to simultaneously perform tokenization, normalization and correction
of Usenet forum posts and . This system relied on a 3-gram language model and
a trainable stateless stochastic transduces as error model, however no
particular details about its implementation were given in the article. In
\cite{choudhury}, Choudhury et al. proposed a modified version of NCM approach
which was specifically targeted at normalization of texting language in
English SMS messages. This model built on the basis of the work by Toutanova
and Moore (\cite{toutanova}) and utilized bigram statistics as language model
for its work. An important change in contrast to the work done by Toutanova
(\cite{toutanova}), however, consisted in the fact, that Choudhury et
al. (\cite{choudhury}) used a joint phone-character HMM lattice for computing
probabilities of restoration suggestions, whereas Toutanova and Moore
(\cite{toutanova}) separately calculated probabilities for phonemic and
graphemic derivations, linearly interpolating them at the end.
